Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-11 paper.tex
Cite Neary et al paper

Experiments were performed in a turbine test bed specifically designd for
cross-flow turbines. The turbine model used in this study was the UNH Reference
Vertical Axis Turbine (RVAT), which was designed to be a generic case for
numerical model testing, similar to the Sandia National Labs/US Department of
Energy RM2 River Turbine, but with higher solidity, or blade chord to radius
ratio.

@@

\todo[inline]{add reference: V. Neary, M. Previsic, R. Jepsen, M. Lawson, Y.
Yu, A. Copping, A. Fontaine, K. Hallett, D. Murray (2014). Methodology for
Design and Economic Analysis of Marine Energy Conversion (MEC) Technologies.
SAND2014-9040}

>>>>

Experiments were performed in a turbine test bed specifically designd for
cross-flow turbines. The turbine model used in this study was the UNH Reference
Vertical Axis Turbine (RVAT), which was designed to be a generic case for
numerical model testing, similar to the Sandia National Labs/US Department of
Energy RM2 River Turbine \cite{Neary2014}, but with higher solidity, or blade
chord to radius ratio.

@@
